TGI-spine

### 2022-04-07 analysis/tgispine_hypotheses.Rmd
informing simulations with pilot data

# The following intervals and mean can be changed to reflect hypotheses
# Cold ratigs: simulation
w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:45,1), sd=15)
a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=15)
w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)

# Warm ratigs: simulation
w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
a_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)

# Burning ratings: simulation
 w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
 w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
 a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:40,1), sd=15)
 a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:30,1), sd=15)
# 
 w_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 w_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)

@@

```{r, echo=FALSE}
library(ez)
library(psychReport)
# burning VAS
burn_anova <- ezANOVA(
  data = df_subj[df_subj$quality == 'burn' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location, stimuli),
  return_aov = TRUE,
  detailed = TRUE
)

# warm VAS
warm_anova <- ezANOVA(
  data = df_subj[df_subj$quality == 'warm' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location, stimuli),
  return_aov = TRUE,
  detailed = TRUE
)

# cold VAS
cold_anova <- ezANOVA(
  data = df_subj[df_subj$quality == 'cold' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location, stimuli),
  return_aov = TRUE,
  detailed = TRUE
)

```{r}
burn_anova
```
```{r}
warm_anova
```
``` {r}
cold_anova
```

>>>>

# The following intervals and mean can be changed to reflect hypotheses
# Cold ratigs: simulation
w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=15)
a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:45,1), sd=15)
w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)

# Warm ratigs: simulation
w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
a_dr_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
a_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)

# Burning ratings: simulation
 w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
 w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
 a_dr_tgi_burn <- rnorm(trialN, mean=sample(5:40,1), sd=15)
 a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:50,1), sd=15)
# 
 w_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 w_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)

@@

```{r, echo=FALSE}
library(ez)
library(psychReport)
# isolate just TGI for purposes of determining effect size
df_tgi <- df_subj[df_subj$stimuli == 'tgi' ,]

# burning VAS
burn_anova <- ezANOVA(
  data = df_tgi[df_tgi$quality == 'burn' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location),
  return_aov = TRUE,
  detailed = TRUE
)

# warm VAS
warm_anova <- ezANOVA(
  data = df_tgi[df_tgi$quality == 'warm' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location),
  return_aov = TRUE,
  detailed = TRUE
)

# cold VAS
cold_anova <- ezANOVA(
  data = df_tgi[df_tgi$quality == 'cold' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location),
  return_aov = TRUE,
  detailed = TRUE
)
